Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
+ Added nice flowchart

@@

\subsection{New approach}
As outlined in the introduction, we combined several ideas for obtaining an inpainting algorithm that provides both good results and fast performance. The input of our algorithm is the image to be restored together with a mask that indicates its unknown spots.\\
Before entering the iterative part of our algorithm, the following three steps are performed (as seen in figure ??):
\begin{enumerate}
\item In order to guide the elimination of frequencies by finding the optimal threshold (as described below), we first remove additional pixels from the image and use them as the validation set. The fraction of additional pixels to be removed is a global parameter, which we optimized using gradient descent (as explained in section ??).
\item Since our reduction in the Fourier space works best with framed patches, we frame the complete image by mirroring its margin. (The size of the frame is another optimizable global parameter.)
\item For obtaining an initial reconstruction of the image, we compute a weighted sum over all the neighboring pixels that are known. By setting all unknown pixels in the image to zero and encoding known values with 1s in the mask, elementwise division of the filtered image by the similarly filtered mask results in a normalized sum weighted by the filtering kernel. (This procedure, which we call Gaussian interpolation, allows us to use MATLAB's fast native functions and to fill holes up to the kernel size, which is another global parameter.)
\end{enumerate}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

\subsection{New approach}

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, inner sep=0pt]

\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=7em, text centered, rounded corners, minimum height=4em]

\tikzstyle{line} = [draw, -latex']

\tikzstyle{cloud} = [draw, ellipse,fill=red!20,
    minimum height=2em]

\begin{tikzpicture}[node distance = 2cm, auto]
  % Place nodes
  \node [cloud] (node1) {Start};
  \node [block, right of=node1, node distance = 3.1cm] (node2) {Remove validation set};
  \node [block, below of=node2] (node3) {Frame image};
  \node [block, below of=node3] (node4) {Gaussian interpolation};
  \node [decision, below of=node4] (node5) {Iterative?};
  \node [block, right of=node5, node distance = 3.1cm, fill=green!20] (node6) {Find best threshold};
  \node [block, below of=node6, fill=green!20] (node7) {Reset known values except validation set};

  \node [block, left of=node5, node distance = 3.1cm] (node8) {Find best threshold};
  \node [block, below of=node8] (node9) {Gaussian interpolation on original data};
  \node [block, below of=node9] (node10) {Apply best threshold};

  \node [block, right of=node10, node distance = 3.1cm] (node11) {Unframe image};
  \node [block, below of=node11] (node12) {Reset known values};
  \node [cloud, right of=node12, node distance = 3.1cm] (node13) {End};

  % Draw edges
  \path [line] (node1) -- (node2);
  \path [line] (node2) -- (node3);
  \path [line] (node3) -- (node4);
  \path [line] (node4) -- (node5);
  \path [line] (node5) -- node[above]{yes} (node6);
  \path [line] (node5) -- node[above]{no} (node8);

  \draw [->] (node6) to [bend left=20] (node7);
  \draw [->] (node7) to [bend left=20] (node6);

  \path [line] (node8) -- (node9);
  \path [line] (node9) -- (node10);
  \path [line] (node10) -- (node11);
  \path [line] (node11) -- (node12);
  \path [line] (node12) -- (node13);

  \path [line] (node7) |- (node11);
\end{tikzpicture}

As outlined in the introduction, we combined several ideas for obtaining an inpainting algorithm that provides both good results and fast performance. The input of our algorithm is the image to be restored together with a mask that indicates its unknown spots.\\
Before entering the iterative part of our algorithm, the following three steps are performed (as seen in figure ??):
\begin{enumerate}
\item In order to guide the elimination of frequencies by finding the optimal threshold (as described below), we first remove additional pixels from the image and use them as the validation set. The fraction of additional pixels to be removed is a global parameter, which we optimized using gradient descent (as explained in section ??).
\item Since our reduction in the Fourier space works best with framed patches, we frame the complete image by mirroring its margin. (The size of the frame is another optimizable global parameter.)
\item For obtaining an initial reconstruction of the image, we compute a weighted sum over all the neighboring pixels that are known. By setting all unknown pixels in the image to zero and encoding known values with 1s in the mask, elementwise division of the filtered image by the similarly filtered mask results in a normalized sum weighted by the filtering kernel. (This procedure, which we call Gaussian interpolation, allows us to use MATLAB's fast native functions and to fill holes up to the kernel size, which is another global parameter.)
\end{enumerate}
